### 2016-10-11 R/ITHIM.Rmd
Update to methods paper

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
install("~/ITHIM/")
library("ITHIM")

@@

```{r compute, echo = FALSE, eval = TRUE}
compute <- TRUE
```

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 25; length <- 10; wd <- upper/length;

@@

@@

```{r roadInjuries, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
convertState <- function( stateCode ){

>>>>

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
library("devtools")
install_github("smbache/magrittr", ref="master")
library("magrittr")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
library("ITHIM")

@@

```{r compute, echo = FALSE, eval = TRUE}
compute <- FALSE
```

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 10; length <- 5; wd <- upper/length;

@@

Do it again, but with quintiles

```{r ITHIMObjsQuintiles, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
DALYsTotal2 <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", seq(1, 9, by = 2)/10 )

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal2 <- rbind(DALYsTotal2, DALYs)
}

DALYsTotal2 <- within(DALYsTotal2, {
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA"))
})

DALYsTotal <- rbind(data.frame(DALYsTotal,quints="Percentiles"), data.frame(DALYsTotal2,quints="Quintiles"))

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Mean Non-Travel METs (MET-hrs./week) (Referent Group)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper)) + facet_grid( . ~ quints)

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Mean Non-Travel METs (MET-hrs./week) (Referent Group)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper)) + geom_point() + facet_grid( . ~ quints)

@@

```{r roadInjuries, eval = FALSE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
convertState <- function( stateCode ){

### 2016-10-11 methodsPaper/tex/abstract.tex
chmod -R 755 .
Update to methods paper

\section{Summary:}

While increased active transportation, primarily cycling and walking,
is often held up as a goal for improved public health --- via reduced
chronic disease, improved air quality, and reductions in greenhouse
gas emissions — obtaining estimates for the quantiative impacts of
such shifts remains infrequent, if not altogether absent from related
policy action. Using U.S. metropolitan counties from seven states we
perform a comparative risk analysis between each regions and national
averages as the baseline.  We employ a portion of the Integrated
Transport and Health Impacts Model (ITHIM) to investigate the reduced
chronic disease burden of ($x$, $y$, $z$ outcomes) from changing
levels of physical activity with population shifts in the amount of
biking and walking done for transport. The analysis is informed by
regional travel parameters from the National Household Transportation
Survey, non-travel activity metrics from the American Time Use Survey,
and baseline disease burden from the Centers for Disease Control and
Prevention's WONDER database and the Global Burden of Disease dataset.
Our findings show that the California and New York State have travel
patterns that, if mirrored by the nation, would save the U.S. upwards
of fifty thousand disability adjusted life years.

%% \section{Availability:}

@@

\section{Supplementary information:}

See \webpage{} for links to the source code, manual, tutorial and
links for more information about the ITHIM model.

\section{Contact:}
\href{javargo@wisc.edu}{javargo@wisc.edu}

>>>>

%% While increased active transportation, primarily cycling and walking,
%% is often held up as a goal for improved public health --- via reduced
%% chronic disease, improved air quality, and reductions in greenhouse
%% gas emissions — obtaining estimates for the quantiative impacts of
%% such shifts remains infrequent, if not altogether absent from related
%% policy action. Using U.S. metropolitan counties from seven states we
%% perform a comparative risk analysis between each regions and national
%% averages as the baseline.  We employ a portion of the Integrated
%% Transport and Health Impacts Model (ITHIM) to investigate the reduced
%% chronic disease burden of ($x$, $y$, $z$ outcomes) from changing
%% levels of physical activity with population shifts in the amount of
%% biking and walking done for transport. The analysis is informed by
%% regional travel parameters from the National Household Transportation
%% Survey, non-travel activity metrics from the American Time Use Survey,
%% and baseline disease burden from the Centers for Disease Control and
%% Prevention's WONDER database and the Global Burden of Disease dataset.
%% Our findings show that the California and New York State have travel
%% patterns that, if mirrored by the nation, would save the U.S. upwards
%% of fifty thousand disability adjusted life years.

%\subsection{Summary:}
%% \section{Availability:}

@@

% \section{Supplementary information:}

% See \webpage{} for links to the source code, manual, tutorial and
% links for more information about the ITHIM model.

% \section{Contact:}
% \href{javargo@wisc.edu}{javargo@wisc.edu}
